%-------------------------
% Resume in Latex
% Author : Alex Salazar
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item[]
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\begin{document}

%----------HEADING----------
    \begin{center}
    {\Huge \scshape Alex Salazar} \\ \vspace{1pt}
    Summerville, SC, United States \\ \vspace{1pt}
    \small \href{mailto:alexsalazarmartinez@gmail.com}{\faEnvelope\ \underline{alexsalazarmartinez@gmail.com}} ~
    \href{https://www.linkedin.com/in/alexander-salazar-375699277}{\faLinkedin\ \underline{linkedin.com/in/alexander-salazar-375699277}}  ~
    \href{https://github.com/saladbaralex}{\faGithub\ \underline{github.com/saladbaralex}}
    \vspace{-8pt}
    \end{center}

%-----------EDUCATION-----------
    \section{Education}
    \begin{itemize}  % Ensure it's inside an itemize environment
        \resumeSubheading{Clemson University}{Aug. 2023 -- May 2026}{Bachelor of Science in Computer Science}{GPA: 3.68 (Spring 2025)}
    \end{itemize}

%------RELEVANT COURSEWORK-------
    \section{Relevant Coursework}
    \begin{multicols}{4}
        \begin{itemize}[itemsep=-5pt, parsep=3pt]
            \item Data Structures
            \item Algorithm Design
            \item Artificial Intelligence
            \item Data Science
            \item Software Development
            \item Machine Learning
            \item Computer Architecture
            \item Systems Programming
        \end{itemize}
    \end{multicols}

%-----------EXPERIENCE-----------
    \section{Experience}
    \begin{itemize}
        \resumeSubheading{Clemson Creative Inquiry Program}{Jan. 2024 -- Present}{Undergraduate Researcher}{Clemson, SC}
        \begin{itemize}
            \item Conducted analysis on privacy policies and integration in software workflows.
            \item Utilized Python, Pandas, and NLTK for dataset processing and text classification.
            \item Developed frameworks to enhance privacy compliance through AI-based models.
        \end{itemize}

        \resumeSubheading{Rio Chico Mexican Restaurant}{Aug. 2022 -- Present}{Server}{Summerville, SC}
        \begin{itemize}
            \item Worked as a team to improve order efficiency and customer satisfaction.
            \item Increased daily sales through customer engagement and promotions.
        \end{itemize}
    \end{itemize}

%-----------PROJECTS-----------
    \section{Projects}
    \begin{itemize}
        \resumeSubheading{Privacy Compliance Research}{Jan. 2024}{Python, NLP, Scikit-learn}{Clemson, SC}
        \begin{itemize}
            \item Researched privacy compliance in software engineering.
            \item Developed AI-driven compliance monitoring using NLP and Scikit-learn.
            \item Analyzed policy documents using text processing techniques.
        \end{itemize}

        \resumeSubheading{Sleep Data Science Project}{Feb. 2025}{Python, Pandas, Matplotlib, Scikit-learn}{Clemson, SC}
        \begin{itemize}
            \item Analyzed sleep patterns using wearable device data.
            \item Built predictive models for sleep quality classification.
            \item Visualized trends and correlations with Matplotlib and Pandas.
        \end{itemize}
    \end{itemize}

%-----------TECHNICAL SKILLS-----------
    \section{Technical Skills}
    \begin{itemize}
        \item \textbf{Languages:} Python, Java, C++
        \item \textbf{Machine Learning:} NumPy, Pandas, Scikit-learn, PyTorch, NLTK
        \item \textbf{Data Science:} Data Visualization, Statistical Analysis, Data Cleaning
        \item \textbf{Development Tools:} Git, Linux, Jupyter Notebook
    \end{itemize}

%-----------HONORS & AWARDS-----------
    \section{Honors \& Awards}
    \begin{itemize}
        \item President's List (Fall 2024) - 4.0 GPA
        \item Dean’s List Academic Achievement Award (Academic
        Year 2023-24, 2024-25)
    \end{itemize}

\end{document}
